---
title: "QC for experiment 1"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
rm(list=ls())

source('./scripts/utils/load_all_libraries.R')

# Some global setup ###########################################################

# flags

save_qc_table  <- T
qc_filter      <- F
which_experiment <- c(1)


```

```{r import-data}
# Read the txt file

source('./scripts/utils/load_transform_tt_data.R')
source('./scripts/utils/load_transform_exp_data.R')

# Filter to only have that experiment paradigm data which we specified above
exp_long <- exp_long %>%
        filter(experiment %in% which_experiment) %>%
        droplevels()

```

Will create a table called qc_table, listing which participants failed which of the checks.

# Check QC for the triplet task:


## Button response sequences:

(code hidden)

```{r qc-check-button-sequence-ideal-observer-comparison}

percentile_threshold <- 5


# Load the ideal observer table
button_press_distr <- import('./results/qc_check_permutations/same_button_press_distributions.RData')


# For each participant, count repetitions of certain length
n_perm <- nrow(button_press_distr)
all_lengths <- c(4,5,6,7,8,9,10)

qc_table_button_seq <- tt_long %>%
                filter(trial_stage != 'practice') %>%
                select(prolific_id,response) %>%
                mutate(response = as.character(response),
                       response = replace_na(response,'_')) %>%
                group_by(prolific_id) %>%
                mutate(response_str = paste(response, collapse = '')) %>% 
                select(prolific_id,response_str) %>% unique() %>%
        ungroup()

for (iL in all_lengths){
        

        # Find same_button_reps
        p_rep <- strrep('p',iL)
        q_rep <- strrep('q',iL)
        
        qc_table_button_seq <- qc_table_button_seq %>%
                group_by(prolific_id) %>%
                mutate(total_rep = nrow(str_locate_all(response_str,p_rep)[[1]]) + nrow(str_locate_all(response_str,q_rep)[[1]]),
                       n_perms_larger = sum(button_press_distr[as.character(iL)][[1]] >= total_rep),
                       perc_perms = n_perms_larger*100/n_perm) %>%
                ungroup()
        
        # Now rename the column
        names(qc_table_button_seq)[names(qc_table_button_seq) == "total_rep"]      <- paste0("total_rep_for_",iL)
        names(qc_table_button_seq)[names(qc_table_button_seq) == "n_perms_larger"] <- paste0("n_perms_larger_for_",iL)
        names(qc_table_button_seq)[names(qc_table_button_seq) == "perc_perms"]     <- paste0("perc_perms_for_",iL)

}

# Classify as pass of fail
qc_table_button_seq <- qc_table_button_seq %>% 
        mutate(qc_fail_button_sequence = ifelse(rowSums(select(qc_table_button_seq,starts_with('perc')) < percentile_threshold) > 0,TRUE,FALSE))

# Create a concise qc table
qc_table <- qc_table_button_seq %>%
        select(prolific_id,qc_fail_button_sequence)
```

## Missing trials:

(code hidden)

```{r qc-check-missing-trials}

# perc_total_missing_allowed <- 20
# 
# n_trials_per_session <- tt_long %>% 
#         filter(trial_stage != 'practice') %>% 
#         count(prolific_id,trial_stage,session) %>%
#         slice(1) %>%
#         select(n) %>% .[[1]]
# 
# qc_table_missing_trials <- tt_long %>% 
#         filter(trial_stage != 'practice') %>%
#         count(prolific_id,trial_stage,session,response) %>% 
#         filter(is.na(response)) %>% 
#         mutate(perc_missed = n*100/n_trials_per_session,
#                qc_fail_missing_trials = ifelse(perc_missed >= perc_total_missing_allowed, TRUE, FALSE)) %>%
#         
# 
# qc_table <- merge(qc_table,select(qc_table_missing_trials,qc_fail_missing_trials),by = 'prolific_id')

```

## Check RT

(code hidden)

```{r qc-check-rt}

rt_threshold      <- 1000
rt_perc_threshold <- 40

qc_table_rt <- tt_long %>%
        filter(trial_stage != 'practice') %>%
        group_by(prolific_id) %>%
        summarise(n_rt_less_than_threshold = sum(rt <= rt_threshold, na.rm = T),
                  perc_rt_less_than_threshold = n_rt_less_than_threshold*100/n(),
                  n = n()) %>%
        mutate(qc_fail_rt = perc_rt_less_than_threshold >= rt_perc_threshold) %>%
        ungroup()

# Combine with the main qc table
qc_table <- merge(qc_table,select(qc_table_rt,prolific_id,qc_fail_rt), by = 'prolific_id')

```


## Technical difficulties or debriefing-based

```{r qc-check-technical-debriefing}

manual_qc <- import('./results/experiments/preprocessed_data/qc_manual_for_breaks_debriefing.csv')

qc_table <- qc_table %>% 
        mutate(qc_fail_manual = case_when(
                prolific_id %in% manual_qc$ID ~ TRUE,
                TRUE ~ FALSE
        ))

```


## Output the resulting table:

```{r qc-table-report}

# Which failed?
qc_table <- qc_table %>%
        rowwise() %>%
        mutate(qc_fail_overall = sum(qc_fail_button_sequence,qc_fail_rt,
                                     qc_fail_manual) > 0)

# Add the counterbalancing column
cb <- tt_long %>% select(prolific_id,experiment,counterbalancing) %>% group_by(prolific_id) %>% slice_head()

qc_table <- merge(qc_table,cb,by = 'prolific_id')


qc_table  %>%
        knitr::kable() %>%
        kable_styling(bootstrap_options = "striped")

# Save qc_table
if (save_qc_table){

        export(qc_table,file = './results/experiments/preprocessed_data/qc_table.csv')


}

```

# Plot a panel per participant

## Triplet task:

```{r plots-per-participant-tt, fig.height=8, fig.width=10, warning=FALSE, message=FALSE}

plot_tt_per_part <- F

if (plot_tt_per_part){
        for (iP in unique(tt_long$prolific_id)){
                print(iP)
                
                
                p1 <-
                        tt_long %>%
                        filter(prolific_id == iP) %>% 
                        ggplot(aes(x=rt,fill=session)) +
                        geom_histogram(color="#e9ecef", alpha=0.6, position = 'identity') + 
                        facet_grid(~trial_stage+session) + 
                        geom_vline(xintercept = 1000,color='red',linetype='dashed') + 
                        ggtitle('Triplet task: RT') + 
                        theme(legend.position = '') + 
                        scale_x_continuous(limits = c(0,5000))
        
                p2 <- 
                        tt_long %>%
                        filter(prolific_id == iP) %>%
                        ggplot(aes(x=response,fill=session)) +
                        geom_histogram(color="#e9ecef", alpha=0.6, 
                                       position = 'identity', stat = 'count') + 
                        facet_grid(~trial_stage+session) + 
                        ggtitle('Triplet task: responses')   + 
                        theme(legend.position = '')
                        
                
                p3 <-   tt_long %>%
                        filter(prolific_id == iP) %>%
                        ggplot(aes(x='',y=correct_numeric)) +
                        geom_violin() +
                        geom_boxplot(width=0.1) +
                        # geom_jitter(width = 0.05,
                        #             height = 0,
                        #             alpha=0.3) +
                        geom_dotplot(binaxis='y',
                                     stackdir='center',
                                     stackratio=1,
                                     dotsize=3,
                                     fill="black") +
                        stat_summary(fun=mean, 
                                     na.rm = TRUE,
                                     geom="point",
                                     shape=20, 
                                     size=5, 
                                     color="blue",
                                     fill="blue") + 
                        # stat_summary(fun.data = mean_cl_normal,
                        #              na.rm = TRUE,
                        #              geom = "errorbar",
                        #              size=1,
                        #              width=0.1,
                        # color='blue') +
                        geom_hline(yintercept = c(0.5,0.8),
                                   linetype = 'dashed') + 
                        facet_grid(~trial_stage+session) +
                        ggtitle('Triplet task: accuracy')
                        
                
                p4 <- 
                        tt_long %>%
                        filter(prolific_id == iP) %>% 
                        mutate(response_numeric = case_when(
                                response == 'p' ~ 1,
                                response == 'q' ~ 2,
                                TRUE ~ 0
                        )) %>%
                        ggplot(aes(x=trial_index,y=response_numeric)) +
                        geom_line() + 
                        facet_grid(~trial_stage+session) + 
                        ggtitle('Triplet task: Patter of responses. P=1, Q=2, 0=Missed')
                
                
                grid.arrange(p1,p2,p3,p4,
                             ncol=1,
                             top=iP)  
                
        }
}

```

## Exposure

```{r per-participant, fig.height=5, fig.width=8, message=FALSE, warning=FALSE}

plot_exp_per_part <- F

if (plot_exp_per_part){
                
        
        
        for (iP in unique(tt_long$prolific_id)){
                print(iP)
        
                p5 <- 
                        exp_long %>%
                        filter(prolific_id == iP) %>%
                        ggplot(aes(x=rt,fill=session)) +
                        geom_histogram(color="#e9ecef", alpha=0.6, position = 'identity') + 
                        facet_grid(~session, labeller = label_both) + 
                        geom_vline(xintercept = 500,color='red',linetype='dashed') + 
                        ggtitle('Same/different task: RT') + 
                        theme(legend.position = '') + 
                        scale_x_continuous(limits = c(0,3000))
        
                p6 <- exp_long %>%
                        filter(prolific_id == iP) %>%
                        ggplot(aes(x=response,fill=session)) +
                        geom_histogram(color="#e9ecef", alpha=0.6, 
                                       position = 'identity', stat = 'count') + 
                        facet_grid(~session, labeller = label_both) + 
                        ggtitle('Same/Different task: responses') + 
                        theme(legend.position = '')
                
                grid.arrange(p5,p6,
                     ncol=1,
                     top=iP) 
                
        }

}

```

# Plot accuracies

## Triplet task

```{r plot-accuracy-triplet-task}
## Average accuracy ---------------------------------------------------
tt_acc <-
        tt_long %>%
        filter(correct_response != '',
               prolific_id != 'selftest') %>%
        select(prolific_id,correct,trial_stage)

# Plot this
tt_acc %>%
        group_by(prolific_id,trial_stage) %>%
        summarise(mean_acc = mean(correct,na.rm=F)) %>%
        ggplot(aes(x=trial_stage,y=mean_acc)) +
        geom_boxplot() +
        geom_point() +
        geom_line(aes(group=prolific_id,color=prolific_id)) +
        ggtitle('Triplet task accuracy')

```

```{r plot-accuracy-triplet-task-separate-priolific-id, fig.width=12, fig.height=3}

tt_acc %>%
        filter(trial_stage != 'practice') %>%
        group_by(prolific_id,trial_stage) %>%
        summarise(mean_acc = mean(correct,na.rm=F)) %>%
        ggplot(aes(x=trial_stage,y=mean_acc)) +
        geom_point() +
        geom_line(aes(group=prolific_id,color=prolific_id)) +
        facet_wrap(~prolific_id, nrow = 2) +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
        ggtitle('Triplet task accuracy')

tt_acc %>%
        filter(trial_stage != 'practice') %>%
        group_by(prolific_id) %>%
        summarise(mean_acc = mean(correct,na.rm=F)) %>%
        ggplot(aes(x=prolific_id,y=mean_acc)) +
        geom_bar(stat = "identity", show.legend = FALSE, alpha = 0.5) +
        geom_point() +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
        coord_cartesian(ylim = c(0.5,1)) +
        ggtitle('Triplet task accuracy')

```


## Triplet task: by triplet easiness

Red dots are mean accuracy. Black dots are individual trials, either correct or incorrect.

Triplet easiness of 8 means that the absolute difference between the dist(query,ref1) and dist(query,ref2) is 8. The higher this difference, the easier it is for participants to spot which of the refs is more similar to the query.

```{r, fig.height = 4, fig.width = 15}
## Accuracy by triplet easiness ----------------------------------------------
tt_long %>%
        filter(correct_response != '',
               trial_stage != 'practice') %>%
        droplevels() %>%
        reorder_levels(triplet_easiness,order = c("0",'8','16')) %>%
        group_by(prolific_id,trial_stage,triplet_easiness) %>%
        summarise(mean_acc = mean(correct,na.rm=F)) %>%
        ggplot(aes(x=triplet_easiness,y=mean_acc)) +
        # geom_bar(stat='identity') +
        # geom_dotplot(mapping = aes(x=triplet_easiness,y=correct),
        #              data=filter(tt_long,correct_response != '',trial_stage != 'practice'),
        #              binaxis='y',
        #              stackdir='centerwhole',
        #              stackratio=1, dotsize=0.5, fill="black") +
        geom_point(color='red') +     
        geom_line(group='prolific_id') +
        facet_grid(trial_stage~prolific_id) +
        ylab('Mean accuracy') +
        ggtitle('Accuracy by triplet easiness')

```
## Triplet task: only QC fail participants

```{r plot-accuracy-triplet-task}

# Qc fail participants
qc_fail_ptp <- qc_table %>% 
        filter(qc_fail_button_sequence == TRUE | qc_fail_rt == TRUE) %>% 
        droplevels() %>%
        select(prolific_id) %>% .[[1]]
        

## Average accuracy ---------------------------------------------------
tt_long %>%
        filter(correct_response != '',
               prolific_id %in% qc_fail_ptp) %>%
        select(prolific_id,correct,trial_stage) %>%
        group_by(prolific_id,trial_stage) %>%
        summarise(mean_acc = mean(correct,na.rm=F)) %>%
        ggplot(aes(x=trial_stage,y=mean_acc)) +
        geom_boxplot() +
        geom_point() +
        geom_line(aes(group=prolific_id,color=prolific_id)) +
        ggtitle('Triplet task accuracy')

```

## Exposure task:

```{r plots-accuracy-exposure}

exp_acc <-
        exp_long %>%
        filter(correct_response != '',
               prolific_id != 'selftest') %>%
        select(prolific_id,correct) %>%
        mutate(correct = as.numeric(correct),
               correct = coalesce(correct,0)) %>%
        group_by(prolific_id) %>%
        summarise(mean_acc = mean(correct,na.rm=F))

exp_acc_by_type <-
        exp_long %>%
        filter(correct_response != '',
               prolific_id != 'selftest') %>%
        select(prolific_id,
               correct_response,
               correct) %>%
        mutate(correct = as.numeric(correct),
               correct = coalesce(correct,0)) %>%
        group_by(prolific_id,correct_response) %>%
        summarise(mean_acc = mean(correct,na.rm=F))

# Plot this
exp_acc %>%
        group_by(prolific_id) %>%
        ggplot(aes(x='identity',y=mean_acc)) +
        geom_boxplot(outlier.shape = '') +
        geom_jitter(width=0.1,aes(color=prolific_id),size=3) +
        ggtitle('Exposure accuracy: overall')

exp_acc_by_type %>%
        group_by(prolific_id) %>%
        ggplot(aes(x=correct_response,y=mean_acc)) +
        geom_boxplot(outlier.shape = '') +
        geom_point() +
        geom_line(aes(group=prolific_id,color=prolific_id)) +
        scale_x_discrete(labels=c('Same','Different')) +
        ggtitle('Exposure accuracy: by trial type')

```

# Table of counterbalancing conditions

```{r counterbalancing-table}



```



```{r}
## Overall accuracy for payment ----------------------------------------------
overall_acc <- rbind(select(tt_acc,prolific_id,correct),exp_acc)

overall_acc %>%
        mutate(correct = as.numeric(correct)) %>%
        group_by(prolific_id) %>%
        get_summary_stats(correct,type='mean_sd') %>%
        mutate(payment = 2*mean) %>% select(prolific_id,payment) %>% View()
        write_csv('payment.csv')

```