---
title: "TT Overall Overview"
output:
  html_document:
    number_sections: false
    
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      knit_root_dir = rprojroot::find_rstudio_root_file(),
      output_file = paste0(
      rprojroot::find_rstudio_root_file(),
      '/results/pilots/',
      'pilot_analysis_plots_for_presentation_',Sys.Date(),'.html'
      ),
      envir = globalenv()
    )
  })
  
  
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)

```

```{r load-libraries}

# Clean the environment and load libraries ############################

rm(list=ls())

pacman::p_load(pacman,
               rio,
               tidyverse,
               rstatix,
               DT,
               kableExtra,
               readr,
               writexl,
               jsonlite,
               stringr,
               gridExtra,
               knitr,
               magrittr,
               Hmisc,
               psycho)

```

# Load the data and set flags

(code hidden)

```{r load-transform-tt-data}

qc_filter <- T
print(paste0('QC filter? ', qc_filter))

which_paradigm <- c(2)
print(paste0('Which pilot paradigm? ', which_paradigm))

source('./scripts/utils/load_transform_tt_data.R')
source('./scripts/utils/load_transform_exp_data.R')
source('./scripts/utils/summary_stats_for_various_factors.R')

# Flags and settings

chose_sparse_color  <- 'blue'
chose_highdim_color <- 'green'
accuracy_color      <- 'yellow'

# Show the basic table
tt_long %>%
        filter(trial_index == 1,session == 1,trial_stage == 'pre_exposure') %>%
        group_by(counterbalancing,
                 prolific_id) %>%
        summarise(n = n()) %>%
        knitr::kable(caption = 'Participants and counterbalancing') %>%
        kable_styling(bootstrap_options = "striped")

```

# Exposure:

```{r exposure}

n_same_resp <- 
        exp_long %>%
        group_by(prolific_id,dist_abs_from_prev,response,.drop=FALSE) %>% 
        summarise(n = n()) %>%
        ungroup() %>%
        filter(response == 'q')


n_tot_resp <- 
        exp_long %>%
        group_by(prolific_id,dist_abs_from_prev) %>%
        summarise(n = n()) %>%
        ungroup()

same_resp_table <- 
        merge(n_same_resp,n_tot_resp,by=c('prolific_id','dist_abs_from_prev')) %>%
        mutate(avg_same_resp = n.x*100/n.y) %>% 
        ungroup()

same_resp_table %>%
        filter(!is.na(dist_abs_from_prev)) %>%
        mutate(dist_abs_from_prev = as.numeric(as.character(dist_abs_from_prev))) %>%
        ggplot(aes(x=dist_abs_from_prev,y=avg_same_resp)) +
        geom_point(size=0.5) +
        geom_line(size=0.5, aes(group=prolific_id,color=prolific_id)) +
        geom_smooth() +
        stat_summary(fun='mean',
                     geom='line',
                     size=1.5,
                     color = 'blue',
                     linetype = 'dashed') +
        scale_y_continuous(breaks=seq(0,100,5)) +
        scale_x_continuous(breaks=seq(0,40,1)) +
        ylab('% "Same" response') +
        xlab('Unit distance from previous') + 
        theme_classic() +
        theme(axis.text.x = element_text(angle = 90),
              legend.position = '') +
        geom_hline(yintercept = 100-75,linetype='dashed') +
        geom_hline(yintercept = 100-50,linetype='dashed') +
        # stat_summary(aes(x=dist_abs_from_prev,y=n.y),
        #              fun='mean',
        #              geom='line',
        #              size=1) + 
        ggtitle('exposure psychometric curves')

same_resp_table %>%
  group_by(prolific_id,dist_abs_from_prev) %>%
  summarise(n = n())


```


# Accuracy

```{r accuracy, fig.width=10, fig.height=4}

fig1 <- tt_part_sum_stats %>%
        filter(dep_var_type != 'post_pre_diff') %>%
        ggplot(aes(x=dep_var_type,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '',
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +     
        stat_summary(fun = mean,
                     color = 'red') + 
        coord_cartesian(ylim = c(0.5,1)) +
        # geom_hline(yintercept = 0, linetype = 'dashed') +         
        ggtitle('accuracy') +
        xlab('') +
        ylab('Accuracy')

fig2 <- tt_part_sum_stats %>%
        filter(dep_var_type != 'post_pre_diff') %>%
        ggplot(aes(x=dep_var_type,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '',
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +    
        stat_summary(fun = mean,
                     color = 'red') + 
        coord_cartesian(ylim = c(0.5,1)) +
        # geom_hline(yintercept = 0, linetype = 'dashed') +         
        facet_wrap(~counterbalancing) +
        xlab('') +
        ylab('Accuracy')

grid.arrange(fig1,fig2,
             nrow = 1,
             widths = 1:2)

```



# Plots over all trials

Show data for Pre, post, and post-minus-pre difference. 
Also, show combined data and broken down by the two counterbalancing conditions (dense_left and dense_right).

These plots do not address the questions we're interested in, because they average over all types of triplets from all templates located anywhere along the dimension.

But its good to see that accuracy is alright: around 75% pre and post.

```{r all-dep-var-overall-plots, fig.width=12, fig.height=10, warning=F}

# Choice towards sparse
fig1 <- tt_part_sum_stats %>%
        #filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=dep_var_type,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +  
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        ggtitle('chose towards sparse') +
        ylab('P(chose sparse)') +
        xlab('')

fig2 <- tt_part_sum_stats %>%
        #filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=dep_var_type,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +        
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        facet_wrap(~counterbalancing)  +
        ylab('P(chose sparse)') +
        xlab('')

#  
fig3 <- tt_part_sum_stats %>%
        #filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=dep_var_type,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +     
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        ggtitle('chose towards high dimension') +
        ylab('P(chose high-simension)') +
        xlab('')

fig4 <- tt_part_sum_stats %>%
        #filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=dep_var_type,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '',
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +    
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        facet_wrap(~counterbalancing) +
        ylab('P(chose high-dimension)') +
        xlab('')

#  
fig5 <- tt_part_sum_stats %>%
        #filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=dep_var_type,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '',
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +     
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        ggtitle('accuracy')

fig6 <- tt_part_sum_stats %>%
        #filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=dep_var_type,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '',
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +    
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        facet_wrap(~counterbalancing)
        
grid.arrange(fig1,fig2,
             fig3,fig4,
             fig5,fig6,
             nrow = 3,
             widths = 1:2)
             
```

# Plots over triplet location

```{r all-dep-var-triplet-location-plots, fig.width=12, fig.height=6, warning=F}

x_font_size <- 10

# Choice towards sparse
fig1 <- tt_part_sum_stats_triplet_location %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +  
        stat_summary(fun = mean,
                     color = 'red') + 
        geom_hline(yintercept = 0, linetype = 'dashed') +      
        theme(text = element_text(size=x_font_size)) + 
        ggtitle('Post-pre P(chose sparse)') + 
        ylab('Post-pre P(chose sparse)')

fig2 <- tt_part_sum_stats_triplet_location %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +        
        stat_summary(fun = mean,
                     color = 'red') + 
        geom_hline(yintercept = 0, linetype = 'dashed') +       
        theme(text = element_text(size=x_font_size)) + 
        facet_wrap(~counterbalancing) + 
        ylab('Post-pre P(chose sparse)')

#  
fig3 <- tt_part_sum_stats_triplet_location %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +     
        stat_summary(fun = mean,
                     color = 'red') + 
        geom_hline(yintercept = 0, linetype = 'dashed') +   
        theme(text = element_text(size=x_font_size)) + 
        ggtitle('Post-pre: P(chose high-dimension)') + 
        ylab('Post-pre P(chose high-dim)')

fig4 <- tt_part_sum_stats_triplet_location %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +    
        stat_summary(fun = mean,
                     color = 'red') + 
        geom_hline(yintercept = 0, linetype = 'dashed') +      
        theme(text = element_text(size=x_font_size)) + 
        facet_wrap(~counterbalancing) + 
        ylab('Post-pre P(chose dim)')
        
grid.arrange(fig1,fig2,
             fig3,fig4,
             nrow = 2,
             widths = 1:2)
             


```

## Plot the difference between the triplet locations

Here, I take the difference between the triplets located in the various density regions. 
We want across_minus_dense or across_minus_sparse to be above 0.

```{r triplet-location-differences, fig.width=12, fig.height=3, warning=F}

x_font_size <- 10
x_font_angle <- 10

# Now plot this
fig1 <- tt_part_sum_stats_triplet_location_differences %>%
        filter(dep_var_type == 'post_pre_diff',
               chose_towards_type == 'chose_towards_sparse') %>% 
        ggplot(aes(x=difference_type,
                   y=difference_value)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        # geom_line(aes(group=prolific_id),
        #           alpha = 0.2) +  
        stat_summary(fun = mean,
                     color = 'red') + 
        stat_summary(fun.data = mean_cl_normal,
             geom = "errorbar",
             size=0.5,
             width=0.1,
             color='red') + 
        geom_hline(yintercept = 0, linetype = 'dashed') +      
        theme(text = element_text(size=x_font_size)) + 
        # facet_wrap(~counterbalancing) +
        theme(axis.text.x = element_text(angle = x_font_angle)) + 
        ggtitle('Post-pre chose towards sparse. Diff scores')

# Now plot this
fig2 <- tt_part_sum_stats_triplet_location_differences %>%
        filter(dep_var_type == 'post_pre_diff',
               chose_towards_type == 'chose_towards_sparse') %>% 
        ggplot(aes(x=difference_type,
                   y=difference_value)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        # geom_line(aes(group=prolific_id),
        #           alpha = 0.2) +  
        stat_summary(fun = mean,
                     color = 'red') + 
        stat_summary(fun.data = mean_cl_normal,
             geom = "errorbar",
             size=0.5,
             width=0.1,
             color='red') + 
        geom_hline(yintercept = 0, linetype = 'dashed') +      
        theme(text = element_text(size=x_font_size)) + 
        facet_wrap(~counterbalancing) +
        theme(axis.text.x = element_text(angle = x_font_angle))


grid.arrange(fig1,fig2,
             nrow = 1,
             widths = 1:2)

```

# Plots over triplet location and easiness

We have 3 levels of "easiness" in our TEMPlates.

- Easiness = 0: these are symmetric templates, where both referents are equally distant from the query.
- Easiness = 8: here, the distance(query,ref1) is 8 units larger than distance(query,ref2). So its easier to see which refs is closer
- Easiness = 16: here, its even more easy to see which ref is closer to query.

So, its useful to check which of these templates are driving the overall effects we see above.

```{r all-dep-var-curve-type-easiness-plots, fig.width=12, fig.height=8, warning=F}

x_font_size <- 10

# Choice towards sparse
fig1 <- tt_part_sum_stats_triplet_location_easiness %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +  
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +   
        facet_wrap(~triplet_easiness, ncol = 1, strip.position = 'right') +
        theme(text = element_text(size=x_font_size)) + 
        ggtitle('Post-pre chose towards sparse')

fig2 <- tt_part_sum_stats_triplet_location_easiness %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +        
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +  
        theme(text = element_text(size=x_font_size)) + 
        facet_grid(triplet_easiness~counterbalancing)
        
grid.arrange(fig1,fig2,
             nrow = 1,
             widths = 1:2)
             


```

## Plot the difference between triplet locations for each easiness level

```{r triplet-location-differences-easiness-levels, fig.width=12, fig.height=6, warning=F}

x_font_size <- 10
x_font_angle <- 10

# Now plot this
fig1 <- tt_part_sum_stats_triplet_location_easiness_differences %>%
        filter(dep_var_type == 'post_pre_diff',
               chose_towards_type == 'chose_towards_sparse') %>% 
        ggplot(aes(x=difference_type,
                   y=difference_value)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        # geom_line(aes(group=prolific_id),
        #           alpha = 0.2) +  
        stat_summary(fun = mean,
                     color = 'red') + 
        stat_summary(fun.data = mean_cl_normal,
             geom = "errorbar",
             size=0.5,
             width=0.1,
             color='red') + 
        geom_hline(yintercept = 0, linetype = 'dashed') +      
        theme(text = element_text(size=x_font_size)) + 
        facet_wrap(~triplet_easiness, ncol = 1, strip.position = 'right') +
        theme(axis.text.x = element_text(angle = x_font_angle)) + 
        ggtitle('Post-pre chose towards sparse. Diff scores')

# Now plot this
fig2 <- tt_part_sum_stats_triplet_location_easiness_differences %>%
        filter(dep_var_type == 'post_pre_diff',
               chose_towards_type == 'chose_towards_sparse') %>% 
        ggplot(aes(x=difference_type,
                   y=difference_value)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        # geom_line(aes(group=prolific_id),
        #           alpha = 0.2) +  
        stat_summary(fun = mean,
                     color = 'red') + 
        stat_summary(fun.data = mean_cl_normal,
             geom = "errorbar",
             size=0.5,
             width=0.1,
             color='red') + 
        geom_hline(yintercept = 0, linetype = 'dashed') +      
        theme(text = element_text(size=x_font_size)) + 
        facet_wrap(~counterbalancing) +
        facet_grid(triplet_easiness~counterbalancing) +
        theme(axis.text.x = element_text(angle = x_font_angle))


grid.arrange(fig1,fig2,
             nrow = 1,
             widths = 1:2)

```


# Plots for each easiness level: triplet location by template

For each easiness level, we have several types of templates. 
So the plots below simply further break down the plots from the previous panel, plotting data for each template separately. 

This is just in case there is a really strong signal showing us that one of the templates is really great while others not.

```{r all-dep-var-triplet-location-template-easiness-plots, fig.width=12, fig.height=7, warning=F}

x_font_size <- 10

for (iE in levels(tt_part_sum_stats_template_triplet_location_easiness$triplet_easiness)){
        print(iE)
        
        # Choice towards sparse
        fig1 <- tt_part_sum_stats_template_triplet_location_easiness %>%
                filter(dep_var_type == 'post_pre_diff',triplet_easiness == iE) %>%  
                ggplot(aes(x=triplet_location,
                           y=mean_chose_towards_sparse)) +
                geom_violin(fill = chose_sparse_color,alpha = 0.2) +
                geom_boxplot(width=0.2,
                             outlier.shape = '', fatten = 4) +
                geom_jitter(width = 0.05,
                            height = 0,
                            alpha = 0.3) + 
                geom_line(aes(group=prolific_id),
                          alpha = 0.2) +  
                stat_summary(fun = mean,
                             color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +   
                facet_wrap(template_distances~triplet_easiness, ncol = 1, strip.position = 'right') +
                theme(text = element_text(size=x_font_size)) +
                ggtitle('Post-pre chose towards sparse')
        
        fig2 <- tt_part_sum_stats_template_triplet_location_easiness %>%
                filter(dep_var_type == 'post_pre_diff',triplet_easiness == iE) %>%  
                ggplot(aes(x=triplet_location,
                           y=mean_chose_towards_sparse)) +
                geom_violin(fill = chose_sparse_color,alpha = 0.2) +
                geom_boxplot(width=0.15,
                             outlier.shape = '', fatten = 4) +
                geom_jitter(width = 0.05,
                            height = 0,
                            alpha = 0.3) +
                geom_line(aes(group=prolific_id),
                          alpha = 0.2) +        
                stat_summary(fun = mean,
                             color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +   
                theme(text = element_text(size=x_font_size)) +
                facet_grid(triplet_easiness+template_distances~counterbalancing)
        
        grid.arrange(fig1,fig2,
                     nrow = 1,
                     widths = 1:2,
                     top = paste0('Easiness = ', iE))

                     
}

```

# Between participant comparisons:

We've already seen these in sections above, where I break it down by dense_left vs dense_right.

But its useful to plot the data from the two counterbalancing groups next to each other, along with 95% confidence intervals for a quick eye-balling of stats.

## Averaging over all triplets:

```{r between-subj-overall, fig.width=10, fig.height=4, warning=F}

ylimits <- c(-0.2,0.2)

fig1 <- tt_part_sum_stats %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        ggtitle('Chose towards sparse')

fig2 <- tt_part_sum_stats %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        ggtitle('Chose towards high dimension')

fig3 <- tt_part_sum_stats %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        ggtitle('Accuracy')
        

grid.arrange(fig1,fig2,fig3,
             nrow = 1,
             top = 'Post minus pre')

```

## Triplet location

If density stretches the psychological space then what we want to see below is the following:

- The probability of choosing towards sparse should increase for both counterbalancing groups.
- The prob of choosing highdimensional referent should increase for dense_left and decrease for dense_right.

```{r between-subj-triplet-location, fig.width=7, fig.height=5, warning=F}

ylimits <- c(-0.4,0.4)

fig1 <- tt_part_sum_stats_triplet_location %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        facet_wrap(~triplet_location) +
        ggtitle('Chose towards sparse')

fig2 <- tt_part_sum_stats_triplet_location %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        facet_wrap(~triplet_location) + 
        ggtitle('Chose towards high dimension')

# fig3 <- tt_part_sum_stats_triplet_location %>%
#         filter(dep_var_type == 'post_pre_diff') %>%
#         ggplot(aes(x=counterbalancing,
#                    y=mean_correct)) +
#         geom_violin(fill = accuracy_color,
#                     alpha = 0.2) +
#         geom_boxplot(width=0.15,
#                      outlier.shape = '', 
#                      fatten = 4) +
#         geom_jitter(width = 0.05,
#                     height = 0,
#                     alpha = 0.3) +
#         stat_summary(fun = mean,
#                      color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
#         stat_summary(fun.data = mean_cl_normal,
#                      geom = "errorbar",
#                      size=0.5,
#                      width=0.1,
#                      color='red') + 
#         coord_cartesian(ylim = ylimits) + 
#         facet_wrap(~triplet_location) + 
#         ggtitle('Accuracy')


grid.arrange(fig1,fig2,
             # fig4,fig5,fig6,
             ncol = 1,
             top = 'Post minus pre')

```

## Triplet location by template breakdown:

```{r between-subj-triplet-location-template, fig.width=8, fig.height=15, warning=F}

ylimits <- c(-1,1)

fig1 <- tt_part_sum_stats_triplet_location_template %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        facet_grid(template_distances~triplet_location) +
        ggtitle('Chose towards sparse')

fig2 <- tt_part_sum_stats_triplet_location_template %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        facet_grid(template_distances~triplet_location) +
        ggtitle('Chose towards high dimension')


grid.arrange(fig1,
             ncol = 1,
             top = 'Post minus pre')

```
















