---
title: "TT Bias to choose high dimension"
output:
  html_document:
    number_sections: false
    
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      knit_root_dir = rprojroot::find_rstudio_root_file(),
      output_file = paste0(
      rprojroot::find_rstudio_root_file(),
      '/results/pilots/',
      'pilot_bias_high_dim_paradigm_2_3_qc_filtered_',Sys.Date(),'.html'

      ),
      envir = globalenv()
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)

```

```{r load-libraries}

# Clean the environment and load libraries ############################

rm(list=ls())

source('./scripts/utils/load_all_libraries.R')

```

# Load the data and set flags

(code hidden)

```{r load-transform-tt-data}

qc_filter <- T
print(paste0('QC filter? ', qc_filter))


which_paradigm <- c(2,3)

print(paste0('Which pilot paradigm? ', which_paradigm))

source('./scripts/utils/load_transform_tt_data.R')
source('./scripts/utils/summary_stats_for_various_factors.R')

# Flags and settings

chose_sparse_color  <- 'blue'
chose_highdim_color <- 'green'
accuracy_color      <- 'yellow'

# Show the basic table
tt_long %>%
        filter(trial_index == 1,session == 1,trial_stage == 'pre_exposure') %>%
        group_by(counterbalancing,
                 prolific_id) %>%
        summarise(n = n()) %>%
        knitr::kable(caption = 'Participants and counterbalancing') %>%
        kable_styling(bootstrap_options = "striped")

```

# Over all trials, pre post and post-pre

Answer: NO.

Neither pre, post, nor post-pre is there a GENERAL bias to choose higher dimension.

```{r all-trials, fig.width=12, fig.height=3, warning=F}

#  
fig3 <- tt_part_sum_stats %>%
        #filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=dep_var_type,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +     
        stat_summary(fun = mean,
                     color = 'red') + 
        stat_summary(fun.data = mean_cl_normal,
             geom = "errorbar",
             size=1,
             width=0.1,
             color='red') +         
        geom_hline(yintercept = c(0,0.5), linetype = 'dashed') +         
        ggtitle('chose towards high dimension')

fig4 <- tt_part_sum_stats %>%
        #filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=dep_var_type,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '',
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +    
        stat_summary(fun = mean,
                     color = 'red') + 
        stat_summary(fun.data = mean_cl_normal,
             geom = "errorbar",
             size=1,
             width=0.1,
             color='red') +         
        geom_hline(yintercept = c(0,0.5), linetype = 'dashed') +         
        facet_wrap(~counterbalancing)

grid.arrange(fig3,fig4,
             nrow = 1,
             widths = 1:2)
             
```

# Curvature:

Ok so concave ones seem to have more of a tendency to choose towards high-dimension.

```{r curvature, fig.width=12, fig.height=3, warning=F}
x_font_size <- 10
fig3 <- tt_part_sum_stats_curve_type %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=curve_type,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +     
        stat_summary(fun = mean,
                     color = 'red') + 
        stat_summary(fun.data = mean_cl_normal,
             geom = "errorbar",
             size=1,
             width=0.1,
             color='red') +          
        geom_hline(yintercept = 0, linetype = 'dashed') +   
        theme(text = element_text(size=x_font_size)) + 
        ggtitle('Post-pre chose towards high dimension')

fig4 <- tt_part_sum_stats_curve_type %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=curve_type,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +    
        stat_summary(fun = mean,
                     color = 'red') + 
        stat_summary(fun.data = mean_cl_normal,
             geom = "errorbar",
             size=1,
             width=0.1,
             color='red') +          
        geom_hline(yintercept = 0, linetype = 'dashed') +      
        theme(text = element_text(size=x_font_size)) + 
        facet_wrap(~counterbalancing)

grid.arrange(fig3,fig4,
             nrow = 1,
             widths = 1:2)

```

# Curvature, by template + easiness

Seems like positive bias for 16_-16, 8_-16 and 24_-16 ones only. Why?

```{r curvature-template-easiness, fig.width=12, fig.height=15, warning=F}
x_font_size <- 10
fig3 <- tt_part_sum_stats_curve_type_template %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=curve_type,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +     
        stat_summary(fun = mean,
                     color = 'red') + 
        stat_summary(fun.data = mean_cl_normal,
             geom = "errorbar",
             size=1,
             width=0.1,
             color='red') +          
        geom_hline(yintercept = 0, linetype = 'dashed') +   
        theme(text = element_text(size=x_font_size)) + 
        facet_wrap(~template_distances, ncol = 1, strip.position = 'right') +
        geom_text(aes(x=0.5,y=1,label=triplet_easiness)) +
        ggtitle('Post-pre chose towards high dimension')

fig4 <- tt_part_sum_stats_curve_type_template %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=curve_type,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +    
        stat_summary(fun = mean,
                     color = 'red') + 
        stat_summary(fun.data = mean_cl_normal,
             geom = "errorbar",
             size=1,
             width=0.1,
             color='red') +          
        geom_hline(yintercept = 0, linetype = 'dashed') +      
        theme(text = element_text(size=x_font_size)) + 
        geom_text(aes(x=0.5,y=1,label=triplet_easiness)) +
        facet_grid(template_distances~counterbalancing)

grid.arrange(fig3,fig4,
             nrow = 1,
             widths = 1:2)

```



# Plots with x axis sorted by diagnosticity

## Y axis: post-pre chose high-dimension

```{r sorted-plot-chose-high-dimension, fig.width=13, fig.height=15}

# For sorted data
fig1 <- tt_long_post_pre_and_diff %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=reorder(triplet_unique_name,-chose_towards_highdim_avg_across_reps),
                   y=chose_towards_highdim_avg_across_reps)) +
        geom_boxplot(fatten = 3, aes(color=curve_type)) + 
        stat_summary(fun=mean,
                     geom = 'point',
                     size = 5,
                     color="black",
                     aes(shape = triplet_easiness)) + 
        geom_hline(yintercept = 0, linetype = 'dashed') +
        theme(axis.text.x = element_text(angle = 90),
              legend.position = 'top') +
        ylab('Post-pre: chose high-dim') + 
        xlab('Individual Triplets') +
        ggtitle('All counterbalancing groups')



fig2 <- tt_long_post_pre_and_diff %>%
        filter(counterbalancing == 'dense_right',
               dep_var_type == 'post_pre_diff') %>% 
         ggplot(aes(x=reorder(triplet_unique_name,-chose_towards_highdim_avg_across_reps),
                   y=chose_towards_highdim_avg_across_reps)) +
        geom_boxplot(fatten = 4,aes(color=curve_type)) + 
        stat_summary(fun=mean,
                     color='black',
                     aes(shape = triplet_easiness),
                     size = 1) + 
        geom_hline(yintercept = 0, linetype = 'dashed') +
        # geom_point(data = filter(tt_bw_part_sum_stats_triplets,counterbalancing == 'dense_right'),
        #            aes(x = triplet_unique_name,
        #                y = mean_chose_towards_sparse)) +
        theme(axis.text.x = element_text(angle = 90),
              legend.position = 'top') +
        ylab('Post-pre: chose high-dim') + 
        xlab('Individual Triplets') +
        ggtitle('Dense Right')

fig3 <- tt_long_post_pre_and_diff %>%
        filter(counterbalancing == 'dense_left',
               dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=reorder(triplet_unique_name,-chose_towards_highdim_avg_across_reps),
                   y=chose_towards_highdim_avg_across_reps)) +
        geom_boxplot(fatten = 4,aes(color=curve_type)) +
        stat_summary(fun=mean,
                     color='black',
                     aes(shape = triplet_easiness),
                     size = 1) + 
        geom_hline(yintercept = 0, linetype = 'dashed') +
        theme(axis.text.x = element_text(angle = 90),
              legend.position = '') +
        ylab('Post-pre: chose high-dim') +
        xlab('Individual Triplets') +
        ggtitle('Dense Left')

grid.arrange(fig1,fig2,fig3,
             nrow = 3)
```

```{r unsorted-plot-chose-high-dimension, fig.width=13, fig.height=15}

# For sorted data
fig1 <- tt_long_post_pre_and_diff %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_unique_name,-chose_towards_highdim_avg_across_reps,
                   y=chose_towards_highdim_avg_across_reps)) +
        geom_boxplot(fatten = 3, aes(color=curve_type)) + 
        stat_summary(fun=mean,
                     geom = 'point',
                     size = 5,
                     color="black",
                     aes(shape = triplet_easiness)) + 
        geom_hline(yintercept = 0, linetype = 'dashed') +
        theme(axis.text.x = element_text(angle = 90),
              legend.position = 'top') +
        ylab('Post-pre: chose high-dim') + 
        xlab('Individual Triplets') +
        ggtitle('All counterbalancing groups')



fig2 <- tt_long_post_pre_and_diff %>%
        filter(counterbalancing == 'dense_right',
               dep_var_type == 'post_pre_diff') %>% 
         ggplot(aes(x=triplet_unique_name,-chose_towards_highdim_avg_across_reps,
                   y=chose_towards_highdim_avg_across_reps)) +
        geom_boxplot(fatten = 4,aes(color=curve_type)) + 
        stat_summary(fun=mean,
                     color='black',
                     aes(shape = triplet_easiness),
                     size = 1) + 
        geom_hline(yintercept = 0, linetype = 'dashed') +
        # geom_point(data = filter(tt_bw_part_sum_stats_triplets,counterbalancing == 'dense_right'),
        #            aes(x = triplet_unique_name,
        #                y = mean_chose_towards_sparse)) +
        theme(axis.text.x = element_text(angle = 90),
              legend.position = 'top') +
        ylab('Post-pre: chose high-dim') + 
        xlab('Individual Triplets') +
        ggtitle('Dense Right')

fig3 <- tt_long_post_pre_and_diff %>%
        filter(counterbalancing == 'dense_left',
               dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=triplet_unique_name,-chose_towards_highdim_avg_across_reps,
                   y=chose_towards_highdim_avg_across_reps)) +
        geom_boxplot(fatten = 4,aes(color=curve_type)) +
        stat_summary(fun=mean,
                     color='black',
                     aes(shape = triplet_easiness),
                     size = 1) + 
        geom_hline(yintercept = 0, linetype = 'dashed') +
        theme(axis.text.x = element_text(angle = 90),
              legend.position = '') +
        ylab('Post-pre: chose high-dim') +
        xlab('Individual Triplets') +
        ggtitle('Dense Left')

grid.arrange(fig1,fig2,fig3,
             nrow = 3)
```



## Y axis: post-pre chose towards higher dimension, between counterbalancing groups

```{r sorted-plot-chose-low-density-cb-differences, fig.width=13, fig.height=20}

fig1 <- tt_bw_part_sum_stats_triplets_difference %>%
        filter(dep_var_type == 'post_pre_diff',
               chose_towards_type == 'chose_towards_highdim') %>%
        ggplot(aes(x=reorder(triplet_unique_name,-difference_value),
                   y=difference_value)) +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        geom_point(aes(color = curve_type,
                       shape = triplet_easiness),
                   size = 3) +
        theme(axis.text.x = element_text(angle = 90),
              legend.position = 'right') +
        ylab('Dense_right - Dense_left') + 
        xlab('Individual Triplets') +
        ggtitle('Post-pre chose high-dimension: Counterbalancing group difference')

fig2 <- tt_bw_part_sum_stats_triplets_difference %>%
        filter(dep_var_type == 'post_pre_diff',
               chose_towards_type == 'chose_towards_highdim') %>%
        ggplot(aes(x=reorder(triplet_unique_name,-abs(difference_value)),
                   y=abs(difference_value))) +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        geom_point(aes(color = curve_type,
                       shape = triplet_easiness),
                   size = 3) +
        theme(axis.text.x = element_text(angle = 90),
              legend.position = 'right') +
        ylab('ABS(Dense_right - Dense_left)') + 
        xlab('Individual Triplets') +
        ggtitle('(SORTED BY ABS) Post-pre chose high-dimension: Counterbalancing group difference')

# Unsorted both groups
fig3 <- tt_long_post_pre_and_diff %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=triplet_unique_name,
                   y=chose_towards_highdim_avg_across_reps,
                   fill=counterbalancing)) +
        geom_boxplot(width = 0.5,
                     fatten = 4,
                     aes(color=curve_type)) +
        stat_summary(fun=mean,
                     color='black',
                     aes(shape = triplet_easiness),
                     size = 0.7,
                     position = position_dodge(width = 0.5)) +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        theme(axis.text.x = element_text(angle = 90),
              legend.position = '') +
        scale_fill_manual(values=c('white','gray')) + 
        ylab('Post-pre: chose high-dim') +
        xlab('Individual Triplets') +
        ggtitle('Both groups')

# Unsorted
fig4 <- tt_bw_part_sum_stats_triplets_difference %>%
        # reorder_levels(triplet_unique_name,order = levels(tt_long_post_pre_and_diff$triplet_unique_name)) %>%
        filter(dep_var_type == 'post_pre_diff',
               chose_towards_type == 'chose_towards_highdim') %>%
        ggplot(aes(x=triplet_unique_name,
                   y=difference_value)) +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        geom_point(aes(color = curve_type,
                       shape = triplet_easiness),
                   size = 3) +
        theme(axis.text.x = element_text(angle = 90),
              legend.position = '') +
        ylab('Dense_right - Dense_left') + 
        xlab('Individual Triplets') +
        ggtitle('(UNSORTED) Post-pre chose high-dimension: Counterbalancing group difference')

# Unsorted absolute value
fig5 <- tt_bw_part_sum_stats_triplets_difference %>%
        filter(dep_var_type == 'post_pre_diff',
               chose_towards_type == 'chose_towards_highdim') %>%
        ggplot(aes(x=triplet_unique_name,
                   y=abs(difference_value))) +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        geom_point(aes(color = curve_type,
                       shape = triplet_easiness),
                   size = 3) +
        theme(axis.text.x = element_text(angle = 90),
              legend.position = '') +
        ylab('ABS(Dense_right - Dense_left)') + 
        xlab('Individual Triplets') +
        ggtitle('(UNSORTED ABS) Post-pre chose high-dimension: Counterbalancing group difference')

grid.arrange(fig1,fig2,fig3,fig4,fig5,
             nrow = 5)

```


<!-- ## Y axis: triplet_location differences in their post-pre value -->

<!-- ```{r sorted-plot-triplet-location-diff-socres-1, fig.width=8, fig.height=15} -->

<!-- # For sorted data -->

<!-- fig1 <- tt_part_sum_stats_triplet_location_template_differences %>% -->
<!--         filter(dep_var_type == 'post_pre_diff', -->
<!--                difference_type == 'across_minus_dense', -->
<!--                chose_towards_type == 'chose_towards_sparse') %>% -->
<!--         ggplot(aes(x=reorder(template_distances,-difference_value), -->
<!--                    y=difference_value)) + -->
<!--         geom_boxplot(fatten = 4,aes(color=template_distances)) +  -->
<!--         stat_summary(fun=mean,color='black', -->
<!--                      aes(shape = triplet_easiness), -->
<!--                      size = 1) +  -->
<!--         geom_hline(yintercept = 0, linetype = 'dashed') + -->
<!--         theme(axis.text.x = element_text(angle = 90), -->
<!--               legend.position = 'right') +  -->
<!--         ylab('Across-Dense:\n Post-pre chose low-density') +  -->
<!--         xlab('Templates') + -->
<!--         ggtitle('Both counterbalancing groups') -->


<!-- fig2 <- tt_part_sum_stats_triplet_location_template_differences %>% -->
<!--         filter(counterbalancing == 'dense_right', -->
<!--                dep_var_type == 'post_pre_diff', -->
<!--                difference_type == 'across_minus_dense', -->
<!--                chose_towards_type == 'chose_towards_sparse') %>% -->
<!--         ggplot(aes(x=reorder(template_distances,-difference_value), -->
<!--                    y=difference_value)) + -->
<!--         geom_boxplot(fatten = 4,aes(color=template_distances)) +  -->
<!--         stat_summary(fun=mean,color='black', -->
<!--                      aes(shape = triplet_easiness), -->
<!--                      size = 1) + -->
<!--         geom_hline(yintercept = 0, linetype = 'dashed') + -->
<!--         theme(axis.text.x = element_text(angle = 90), -->
<!--               legend.position = '') +  -->
<!--         ylab('Across-Dense:\n Post-pre chose low-density') +  -->
<!--         xlab('Templates') + -->
<!--         ggtitle('Dense Right') -->

<!-- fig3 <- tt_part_sum_stats_triplet_location_template_differences %>% -->
<!--         filter(counterbalancing == 'dense_left', -->
<!--                dep_var_type == 'post_pre_diff', -->
<!--                difference_type == 'across_minus_dense', -->
<!--                chose_towards_type == 'chose_towards_sparse') %>% -->
<!--         ggplot(aes(x=reorder(template_distances,-difference_value), -->
<!--                    y=difference_value)) + -->
<!--         geom_boxplot(fatten = 4,aes(color=template_distances)) +  -->
<!--         stat_summary(fun=mean,color='black', -->
<!--                      aes(shape = triplet_easiness), -->
<!--                      size = 1) + -->
<!--         geom_hline(yintercept = 0, linetype = 'dashed') + -->
<!--         theme(axis.text.x = element_text(angle = 90), -->
<!--               legend.position = '') +  -->
<!--         ylab('Across-Dense:\n Post-pre chose low-density') +  -->
<!--         xlab('Templates') + -->
<!--         ggtitle('Dense Left') -->


<!-- grid.arrange(fig1,fig2,fig3, -->
<!--              nrow = 3, -->
<!--              top = 'Across - Dense') -->
<!-- ``` -->

<!-- ```{r sorted-plot-triplet-location-diff-socres-2, fig.width=8, fig.height=15} -->

<!-- # For sorted data -->

<!-- fig1 <- tt_part_sum_stats_triplet_location_template_differences %>% -->
<!--         filter(dep_var_type == 'post_pre_diff', -->
<!--                difference_type == 'across_minus_sparse', -->
<!--                chose_towards_type == 'chose_towards_sparse') %>% -->
<!--         ggplot(aes(x=reorder(template_distances,-difference_value), -->
<!--                    y=difference_value)) + -->
<!--         geom_boxplot(fatten = 4,aes(color=template_distances)) +  -->
<!--         stat_summary(fun=mean,color='black', -->
<!--                      aes(shape = triplet_easiness), -->
<!--                      size = 1) +  -->
<!--         geom_hline(yintercept = 0, linetype = 'dashed') + -->
<!--         theme(axis.text.x = element_text(angle = 90), -->
<!--               legend.position = 'right') +  -->
<!--         ylab('Across-Sparse:\n Post-pre chose low-density') +  -->
<!--         xlab('Templates') + -->
<!--         ggtitle('Both counterbalancing groups') -->


<!-- fig2 <- tt_part_sum_stats_triplet_location_template_differences %>% -->
<!--         filter(counterbalancing == 'dense_right', -->
<!--                dep_var_type == 'post_pre_diff', -->
<!--                difference_type == 'across_minus_sparse', -->
<!--                chose_towards_type == 'chose_towards_sparse') %>% -->
<!--         ggplot(aes(x=reorder(template_distances,-difference_value), -->
<!--                    y=difference_value)) + -->
<!--         geom_boxplot(fatten = 4,aes(color=template_distances)) +  -->
<!--         stat_summary(fun=mean,color='black', -->
<!--                      aes(shape = triplet_easiness), -->
<!--                      size = 1) + -->
<!--         geom_hline(yintercept = 0, linetype = 'dashed') + -->
<!--         theme(axis.text.x = element_text(angle = 90), -->
<!--               legend.position = '') +  -->
<!--         ylab('Across-Sparse:\n Post-pre chose low-density') +  -->
<!--         xlab('Templates') + -->
<!--         ggtitle('Dense Right') -->

<!-- fig3 <- tt_part_sum_stats_triplet_location_template_differences %>% -->
<!--         filter(counterbalancing == 'dense_left', -->
<!--                dep_var_type == 'post_pre_diff', -->
<!--                difference_type == 'across_minus_sparse', -->
<!--                chose_towards_type == 'chose_towards_sparse') %>% -->
<!--         ggplot(aes(x=reorder(template_distances,-difference_value), -->
<!--                    y=difference_value)) + -->
<!--         geom_boxplot(fatten = 4,aes(color=template_distances)) +  -->
<!--         stat_summary(fun=mean,color='black', -->
<!--                      aes(shape = triplet_easiness), -->
<!--                      size = 1) + -->
<!--         geom_hline(yintercept = 0, linetype = 'dashed') + -->
<!--         theme(axis.text.x = element_text(angle = 90), -->
<!--               legend.position = '') +  -->
<!--         ylab('Across-Sparse:\n Post-pre chose low-density') +  -->
<!--         xlab('Templates') + -->
<!--         ggtitle('Dense Left') -->


<!-- grid.arrange(fig1,fig2,fig3, -->
<!--              nrow = 3, -->
<!--              top = 'Across - Sparse') -->
<!-- ``` -->

