---
title: "TT Overall Overview"
output:
  html_document:
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)

```

```{r load-libraries}

# Clean the environment and load libraries ############################

rm(list=ls())

pacman::p_load(pacman,
               rio,
               tidyverse,
               rstatix,
               DT,
               kableExtra,
               readr,
               writexl,
               jsonlite,
               stringr,
               gridExtra,
               knitr,
               magrittr,
               Hmisc,
               psycho)

```

```{r load-transform-tt-data}

qc_filter <- T
print(paste0('QC filter? ', qc_filter))

which_paradigm <- 2
print(paste0('Which pilot paradigm? ', which_paradigm))

source('./scripts/utils/load_transform_tt_data.R')

# Flags and settings

chose_sparse_color  <- 'blue'
chose_highdim_color <- 'green'
accuracy_color      <- 'yellow'

# Show the basic table
tt_long %>%
        filter(trial_index == 1,session == 1,trial_stage == 'pre_exposure') %>%
        group_by(counterbalancing,
                 prolific_id) %>%
        summarise(n = n()) %>%
        knitr::kable(caption = 'Participants and counterbalancing') %>%
        kable_styling(bootstrap_options = "striped")

```

# Summary stats for various combinations of factors.

(Code hidden)
Calculates some tables for plotting them below.

```{r part-specific-summary-stats}

# Create participant summary stats
tt_participant_summary_stats <- tt_long_post_pre_and_diff %>%
        group_by(prolific_id,
                 counterbalancing,
                 dep_var_type) %>%
        summarise(n_datapoints = n(),
                  mean_choice_sum = mean(choice_numeric_sum_across_reps),
                  mean_chose_towards_sparse = mean(chose_towards_sparse_avg_across_reps),
                  mean_chose_towards_highdim = mean(chose_towards_highdim_avg_across_reps),
                  mean_correct = mean(correct_avg_across_reps, na.rm = T)) %>%
        ungroup()

tt_participant_summary_stats_triplet_location <- tt_long_post_pre_and_diff %>%
        group_by(prolific_id,
                 counterbalancing,
                 triplet_location,
                 dep_var_type) %>%
        summarise(n_datapoints = n(),
                  mean_choice_sum = mean(choice_numeric_sum_across_reps),
                  mean_chose_towards_sparse = mean(chose_towards_sparse_avg_across_reps),
                  mean_chose_towards_highdim = mean(chose_towards_highdim_avg_across_reps),
                  mean_correct = mean(correct_avg_across_reps, na.rm = T)) %>%
        ungroup()

tt_participant_summary_stats_curve_type <- tt_long_post_pre_and_diff %>%
        group_by(prolific_id,
                 counterbalancing,
                 curve_type,
                 dep_var_type) %>%
        summarise(n_datapoints = n(),
                  mean_choice_sum = mean(choice_numeric_sum_across_reps),
                  mean_chose_towards_sparse = mean(chose_towards_sparse_avg_across_reps),
                  mean_chose_towards_highdim = mean(chose_towards_highdim_avg_across_reps),
                  mean_correct = mean(correct_avg_across_reps, na.rm = T)) %>%
        ungroup()

tt_participant_summary_stats_triplet_location_easiness <- tt_long_post_pre_and_diff %>%
        group_by(prolific_id,
                 counterbalancing,
                 triplet_location,
                 triplet_easiness,
                 dep_var_type) %>%
        summarise(n_datapoints = n(),
                  mean_choice_sum = mean(choice_numeric_sum_across_reps),
                  mean_chose_towards_sparse = mean(chose_towards_sparse_avg_across_reps),
                  mean_chose_towards_highdim = mean(chose_towards_highdim_avg_across_reps),
                  mean_correct = mean(correct_avg_across_reps, na.rm = T)) %>%
        ungroup()

tt_participant_summary_stats_template_triplet_location_easiness <- tt_long_post_pre_and_diff %>%
        group_by(prolific_id,
                 counterbalancing,
                 template_distances,
                 triplet_location,
                 triplet_easiness,
                 dep_var_type) %>%
        summarise(n_datapoints = n(),
                  mean_choice_sum = mean(choice_numeric_sum_across_reps),
                  mean_chose_towards_sparse = mean(chose_towards_sparse_avg_across_reps),
                  mean_chose_towards_highdim = mean(chose_towards_highdim_avg_across_reps),
                  mean_correct = mean(correct_avg_across_reps, na.rm = T)) %>%
        ungroup()

tt_participant_summary_stats_curve_type_template <- tt_long_post_pre_and_diff %>%
        group_by(prolific_id,
                 counterbalancing,
                 curve_type,
                 template_distances,
                 dep_var_type) %>%
        summarise(n_datapoints = n(),
                  mean_choice_sum = mean(choice_numeric_sum_across_reps),
                  mean_chose_towards_sparse = mean(chose_towards_sparse_avg_across_reps),
                  mean_chose_towards_highdim = mean(chose_towards_highdim_avg_across_reps),
                  mean_correct = mean(correct_avg_across_reps, na.rm = T)) %>%
        ungroup()

tt_participant_summary_stats_triplet_location_template <- tt_long_post_pre_and_diff %>%
        group_by(prolific_id,
                 counterbalancing,
                 triplet_location,
                 template_distances,
                 dep_var_type) %>%
        summarise(n_datapoints = n(),
                  mean_choice_sum = mean(choice_numeric_sum_across_reps),
                  mean_chose_towards_sparse = mean(chose_towards_sparse_avg_across_reps),
                  mean_chose_towards_highdim = mean(chose_towards_highdim_avg_across_reps),
                  mean_correct = mean(correct_avg_across_reps, na.rm = T)) %>%
        ungroup()

```

# Plots over all trials

Show data for Pre, post, and post-minus-pre difference. 
Also, show combined data and broken down by the two counterbalancing conditions (dense_left and dense_right).

These plots do not address the questions we're interested in, because they average over all types of triplets from all templates located anywhere along the dimension.

But its good to see that accuracy is alright: around 75% pre and post.

```{r all-dep-var-overall-plots, fig.width=12, fig.height=10, warning=F}

# Choice towards sparse
fig1 <- tt_participant_summary_stats %>%
        #filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=dep_var_type,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +  
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        ggtitle('chose towards sparse')

fig2 <- tt_participant_summary_stats %>%
        #filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=dep_var_type,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +        
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        facet_wrap(~counterbalancing) 

#  
fig3 <- tt_participant_summary_stats %>%
        #filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=dep_var_type,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +     
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        ggtitle('chose towards high dimension')

fig4 <- tt_participant_summary_stats %>%
        #filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=dep_var_type,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '',
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +    
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        facet_wrap(~counterbalancing)

#  
fig5 <- tt_participant_summary_stats %>%
        #filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=dep_var_type,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '',
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +     
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        ggtitle('accuracy')

fig6 <- tt_participant_summary_stats %>%
        #filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=dep_var_type,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '',
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +    
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        facet_wrap(~counterbalancing)
        
grid.arrange(fig1,fig2,
             fig3,fig4,
             fig5,fig6,
             nrow = 3,
             widths = 1:2)
             
```

# Plots over triplet location

Below, we are already examining our crucial contrast: did the "behavior change post vs pre" differ for triplets in the sparse/dense/middle areas? 

If we look at the left column of plots, averaging over the 2 counterbalancing conditions, we see that in the middle regions, the probability to "choose towards sparse" increases post vs pre-exposure. This increase is larger for the middle regions than the outer ones. 
But looking at the counterbalancing groups, this effect might be driven by the dense_right subgroup.

Looking at the green plots of the probability to choose referent towards the high dimension values:
we see that most data points are above 0, meaning that there is an overall bias post-exposure to choose referents in the high dimension. This bias is counteracted in the dense_right subgroup for the triplets in the "across_density_region" location.

```{r all-dep-var-triplet-location-plots, fig.width=12, fig.height=10, warning=F}

x_font_size <- 10

# Choice towards sparse
fig1 <- tt_participant_summary_stats_triplet_location %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +  
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +      
        theme(text = element_text(size=x_font_size)) + 
        ggtitle('Post-pre chose towards sparse')

fig2 <- tt_participant_summary_stats_triplet_location %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +        
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +       
        theme(text = element_text(size=x_font_size)) + 
        facet_wrap(~counterbalancing) 

#  
fig3 <- tt_participant_summary_stats_triplet_location %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +     
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +   
        theme(text = element_text(size=x_font_size)) + 
        ggtitle('Post-pre chose towards high dimension')

fig4 <- tt_participant_summary_stats_triplet_location %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +    
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +      
        theme(text = element_text(size=x_font_size)) + 
        facet_wrap(~counterbalancing)

#  
fig5 <- tt_participant_summary_stats_triplet_location %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +     
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +  
        theme(text = element_text(size=x_font_size)) + 
        ggtitle('Post-pre accuracy')

fig6 <- tt_participant_summary_stats_triplet_location %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +    
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +  
        theme(text = element_text(size=x_font_size)) + 
        facet_wrap(~counterbalancing)
        
grid.arrange(fig1,fig2,
             fig3,fig4,
             fig5,fig6,
             nrow = 3,
             widths = 1:2)
             


```

# Plots over curve type

I categorize triplets as being either in the concave region, convex region, or in the middle.

The plots below show data largely similar to the above panel. But its more intuitive that for both counterbalancing groups, on the x axis going from left-to-right corresponds to going from left-to-right on the actual dimension axis of the stimuli.

```{r all-dep-var-curve-type-plots, fig.width=12, fig.height=10, warning=F}

# Choice towards sparse
fig1 <- tt_participant_summary_stats_curve_type %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=curve_type,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +  
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        ggtitle('Post-pre chose towards sparse')

fig2 <- tt_participant_summary_stats_curve_type %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=curve_type,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +        
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        facet_wrap(~counterbalancing) 

#  
fig3 <- tt_participant_summary_stats_curve_type %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=curve_type,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +     
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        ggtitle('Post-pre chose towards high dimension')

fig4 <- tt_participant_summary_stats_curve_type %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=curve_type,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +    
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        facet_wrap(~counterbalancing)

#  
fig5 <- tt_participant_summary_stats_curve_type %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=curve_type,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +     
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        ggtitle('Post-pre accuracy')

fig6 <- tt_participant_summary_stats_curve_type %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=curve_type,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +    
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        facet_wrap(~counterbalancing)
        
grid.arrange(fig1,fig2,
             fig3,fig4,
             fig5,fig6,
             nrow = 3,
             widths = 1:2)
             


```

# Plots over curve type and easiness

We have 3 levels of "easiness" in our TEMPlates.

- Easiness = 0: these are symmetric templates, where both referents are equally distant from the query.
- Easiness = 8: here, the distance(query,ref1) is 8 units larger than distance(query,ref2). So its easier to see which refs is closer
- Easiness = 16: here, its even more easy to see which ref is closer to query.

So, its useful to check which of these templates are driving the overall effects we see above.

It seems like its the templates wiht easiness=0 and easiness=8. For easiness=16, the post-pre difference is essentially 0.

```{r all-dep-var-curve-type-easiness-plots, fig.width=12, fig.height=18, warning=F}

x_font_size <- 10

# Choice towards sparse
fig1 <- tt_participant_summary_stats_triplet_location_easiness %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +  
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +   
        facet_wrap(~triplet_easiness, ncol = 1, strip.position = 'right') +
        theme(text = element_text(size=x_font_size)) + 
        ggtitle('Post-pre chose towards sparse')

fig2 <- tt_participant_summary_stats_triplet_location_easiness %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +        
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +  
        theme(text = element_text(size=x_font_size)) + 
        facet_grid(triplet_easiness~counterbalancing)

#  
fig3 <- tt_participant_summary_stats_triplet_location_easiness %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +     
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +     
        facet_wrap(~triplet_easiness, ncol = 1, strip.position = 'right') +
        theme(text = element_text(size=x_font_size)) + 
        ggtitle('Post-pre chose towards high dimension')

fig4 <- tt_participant_summary_stats_triplet_location_easiness %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +    
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +         
        theme(text = element_text(size=x_font_size)) + 
        facet_grid(triplet_easiness~counterbalancing)

#  
fig5 <- tt_participant_summary_stats_triplet_location_easiness %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,alpha = 0.2) +
        geom_boxplot(width=0.2,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) + 
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +     
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        theme(text = element_text(size=x_font_size)) + 
        facet_wrap(~triplet_easiness, ncol = 1, strip.position = 'right') +
        ggtitle('Post-pre accuracy')

fig6 <- tt_participant_summary_stats_triplet_location_easiness %>%
        filter(dep_var_type == 'post_pre_diff') %>% 
        ggplot(aes(x=triplet_location,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +    
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +      
        theme(text = element_text(size=x_font_size)) + 
        facet_grid(triplet_easiness~counterbalancing)
        
grid.arrange(fig1,fig2,
             fig3,fig4,
             fig5,fig6,
             nrow = 3,
             widths = 1:2)
             


```

# Plots for each easiness level: triplet location by template

For each easiness level, we have several types of templates. 
So the plots below simply further break down the plots from the previous panel, plotting data for each template separately. 

This is just in case there is a really strong signal showing us that one of the templates is really great while others not.

I think the data is too noisy here.


```{r all-dep-var-triplet-location-template-easiness-plots, fig.width=12, fig.height=23, warning=F}

x_font_size <- 10

for (iE in levels(tt_participant_summary_stats_template_triplet_location_easiness$triplet_easiness)){
        print(iE)
        
        # Choice towards sparse
        fig1 <- tt_participant_summary_stats_template_triplet_location_easiness %>%
                filter(dep_var_type == 'post_pre_diff',triplet_easiness == iE) %>%  
                ggplot(aes(x=triplet_location,
                           y=mean_chose_towards_sparse)) +
                geom_violin(fill = chose_sparse_color,alpha = 0.2) +
                geom_boxplot(width=0.2,
                             outlier.shape = '', fatten = 4) +
                geom_jitter(width = 0.05,
                            height = 0,
                            alpha = 0.3) + 
                geom_line(aes(group=prolific_id),
                          alpha = 0.2) +  
                stat_summary(fun = mean,
                             color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +   
                facet_wrap(template_distances~triplet_easiness, ncol = 1, strip.position = 'right') +
                theme(text = element_text(size=x_font_size)) +
                ggtitle('Post-pre chose towards sparse')
        
        fig2 <- tt_participant_summary_stats_template_triplet_location_easiness %>%
                filter(dep_var_type == 'post_pre_diff',triplet_easiness == iE) %>%  
                ggplot(aes(x=triplet_location,
                           y=mean_chose_towards_sparse)) +
                geom_violin(fill = chose_sparse_color,alpha = 0.2) +
                geom_boxplot(width=0.15,
                             outlier.shape = '', fatten = 4) +
                geom_jitter(width = 0.05,
                            height = 0,
                            alpha = 0.3) +
                geom_line(aes(group=prolific_id),
                          alpha = 0.2) +        
                stat_summary(fun = mean,
                             color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +   
                theme(text = element_text(size=x_font_size)) +
                facet_grid(triplet_easiness+template_distances~counterbalancing)
        
        #  
        fig3 <- tt_participant_summary_stats_template_triplet_location_easiness %>%
                filter(dep_var_type == 'post_pre_diff',triplet_easiness == iE) %>%  
                ggplot(aes(x=triplet_location,
                           y=mean_chose_towards_highdim)) +
                geom_violin(fill = chose_highdim_color,alpha = 0.2) +
                geom_boxplot(width=0.2,
                             outlier.shape = '', fatten = 4) +
                geom_jitter(width = 0.05,
                            height = 0,
                            alpha = 0.3) + 
                geom_line(aes(group=prolific_id),
                          alpha = 0.2) +     
                stat_summary(fun = mean,
                             color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +     
                facet_wrap(template_distances~triplet_easiness, ncol = 1, strip.position = 'right') +
                theme(text = element_text(size=x_font_size)) +
                ggtitle('Post-pre chose towards high dimension')
        
        fig4 <- tt_participant_summary_stats_template_triplet_location_easiness %>%
                filter(dep_var_type == 'post_pre_diff',triplet_easiness == iE) %>%  
                ggplot(aes(x=triplet_location,
                           y=mean_chose_towards_highdim)) +
                geom_violin(fill = chose_highdim_color,alpha = 0.2) +
                geom_boxplot(width=0.15,
                             outlier.shape = '', fatten = 4) +
                geom_jitter(width = 0.05,
                            height = 0,
                            alpha = 0.3) +
                geom_line(aes(group=prolific_id),
                          alpha = 0.2) +    
                stat_summary(fun = mean,
                             color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +      
                theme(text = element_text(size=x_font_size)) +
                facet_grid(triplet_easiness+template_distances~counterbalancing)
        
        if (iE > 0){
        #  
                fig5 <- tt_participant_summary_stats_template_triplet_location_easiness %>%
                        filter(dep_var_type == 'post_pre_diff',triplet_easiness == iE) %>%
                        ggplot(aes(x=triplet_location,
                                   y=mean_correct)) +
                        geom_violin(fill = accuracy_color,alpha = 0.2) +
                        geom_boxplot(width=0.2,
                                     outlier.shape = '', fatten = 4) +
                        geom_jitter(width = 0.05,
                                    height = 0,
                                    alpha = 0.3) +
                        geom_line(aes(group=prolific_id),
                                  alpha = 0.2) +
                        stat_summary(fun = mean,
                                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +
                        facet_wrap(template_distances~triplet_easiness, ncol = 1, strip.position = 'right') +
                        theme(text = element_text(size=x_font_size)) +
                        ggtitle('Post-pre accuracy')
        
                fig6 <- tt_participant_summary_stats_template_triplet_location_easiness %>%
                        filter(dep_var_type == 'post_pre_diff',triplet_easiness == iE) %>%
                        ggplot(aes(x=triplet_location,
                                   y=mean_correct)) +
                        geom_violin(fill = accuracy_color,alpha = 0.2) +
                        geom_boxplot(width=0.15,
                                     outlier.shape = '', fatten = 4) +
                        geom_jitter(width = 0.05,
                                    height = 0,
                                    alpha = 0.3) +
                        geom_line(aes(group=prolific_id),
                                  alpha = 0.2) +
                        stat_summary(fun = mean,
                                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +
                        theme(text = element_text(size=x_font_size)) +
                        facet_grid(triplet_easiness+template_distances~counterbalancing)
                grid.arrange(fig1,fig2,
                             fig3,fig4,
                             fig5,fig6,
                             nrow = 3,
                             widths = 1:2,
                             top = paste0('Easiness = ', iE))
                
        } else {
                grid.arrange(fig1,fig2,
                             fig3,fig4,
                             nrow = 2,
                             widths = 1:2,
                             top = paste0('Easiness = ', iE))                
        }

                     
}

```

# Between participant comparisons:

We've already seen these in sections above, where I break it down by dense_left vs dense_right.

But its useful to plot the data from the two counterbalancing groups next to each other, along with 95% confidence intervals for a quick eye-balling of stats.

## Averaging over all triplets:

```{r between-subj-overall, fig.width=10, fig.height=4, warning=F}

ylimits <- c(-0.2,0.2)

fig1 <- tt_participant_summary_stats %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        ggtitle('Chose towards sparse')

fig2 <- tt_participant_summary_stats %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        ggtitle('Chose towards high dimension')

fig3 <- tt_participant_summary_stats %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        ggtitle('Accuracy')
        

grid.arrange(fig1,fig2,fig3,
             nrow = 1,
             top = 'Post minus pre')

```

## Curve type breakdown:

If density stretches the psychological space then what we want to see below is the following:

- The probability of choosing towards sparse should increase for both counterbalancing groups.
- The prob of choosing highdimensional referent should increase for dense_left and decrease for dense_right.

We see the above pattern but only for the triplets located across the density boundary!

```{r between-subj-curve-type, fig.width=7, fig.height=8, warning=F}

ylimits <- c(-0.4,0.4)

fig1 <- tt_participant_summary_stats_curve_type %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        facet_wrap(~curve_type) +
        ggtitle('Chose towards sparse')

fig2 <- tt_participant_summary_stats_curve_type %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        facet_wrap(~curve_type) + 
        ggtitle('Chose towards high dimension')

fig3 <- tt_participant_summary_stats_curve_type %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        facet_wrap(~curve_type) + 
        ggtitle('Accuracy')


grid.arrange(fig1,fig2,fig3,
             # fig4,fig5,fig6,
             ncol = 1,
             top = 'Post minus pre')

```

## Triplet location

Similar to the breakdown by curve type in the previous panel.

```{r between-subj-triplet-location, fig.width=7, fig.height=8, warning=F}

ylimits <- c(-0.4,0.4)

fig1 <- tt_participant_summary_stats_triplet_location %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        facet_wrap(~triplet_location) +
        ggtitle('Chose towards sparse')

fig2 <- tt_participant_summary_stats_triplet_location %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        facet_wrap(~triplet_location) + 
        ggtitle('Chose towards high dimension')

fig3 <- tt_participant_summary_stats_triplet_location %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_correct)) +
        geom_violin(fill = accuracy_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        facet_wrap(~triplet_location) + 
        ggtitle('Accuracy')


grid.arrange(fig1,fig2,fig3,
             # fig4,fig5,fig6,
             ncol = 1,
             top = 'Post minus pre')

```

## Triplet location by template breakdown:

Now here, its interesting to see which of the templates are driving the effect in the "across_density_regions" plots. 

It seems to be again the ones that are either symmetric, or easiness=8

```{r between-subj-triplet-location-template, fig.width=8, fig.height=30, warning=F}

ylimits <- c(-1,1)

fig1 <- tt_participant_summary_stats_triplet_location_template %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_chose_towards_sparse)) +
        geom_violin(fill = chose_sparse_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        facet_grid(template_distances~triplet_location) +
        ggtitle('Chose towards sparse')

fig2 <- tt_participant_summary_stats_triplet_location_template %>%
        filter(dep_var_type == 'post_pre_diff') %>%
        ggplot(aes(x=counterbalancing,
                   y=mean_chose_towards_highdim)) +
        geom_violin(fill = chose_highdim_color,
                    alpha = 0.2) +
        geom_boxplot(width=0.15,
                     outlier.shape = '', 
                     fatten = 4) +
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.3) +
        stat_summary(fun = mean,
                     color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=0.5,
                     width=0.1,
                     color='red') + 
        coord_cartesian(ylim = ylimits) + 
        facet_grid(template_distances~triplet_location) +
        ggtitle('Chose towards high dimension')


grid.arrange(fig1,fig2,
             # fig4,fig5,fig6,
             ncol = 1,
             top = 'Post minus pre')

```


<!-- ## Curve type by template breakdown: -->

<!-- ```{r between-subj-curve-type-template, fig.width=8, fig.height=30, warning=F} -->

<!-- ylimits <- c(-1,1) -->

<!-- fig1 <- tt_participant_summary_stats_curve_type_template %>% -->
<!--         filter(dep_var_type == 'post_pre_diff') %>% -->
<!--         ggplot(aes(x=counterbalancing, -->
<!--                    y=mean_chose_towards_sparse)) + -->
<!--         geom_violin(fill = chose_sparse_color, -->
<!--                     alpha = 0.2) + -->
<!--         geom_boxplot(width=0.15, -->
<!--                      outlier.shape = '',  -->
<!--                      fatten = 4) + -->
<!--         geom_jitter(width = 0.05, -->
<!--                     height = 0, -->
<!--                     alpha = 0.3) + -->
<!--         stat_summary(fun = mean, -->
<!--                      color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +  -->
<!--         stat_summary(fun.data = mean_cl_normal, -->
<!--                      geom = "errorbar", -->
<!--                      size=0.5, -->
<!--                      width=0.1, -->
<!--                      color='red') +  -->
<!--         coord_cartesian(ylim = ylimits) +  -->
<!--         facet_grid(template_distances~curve_type) + -->
<!--         ggtitle('Chose towards sparse') -->

<!-- fig2 <- tt_participant_summary_stats_curve_type_template %>% -->
<!--         filter(dep_var_type == 'post_pre_diff') %>% -->
<!--         ggplot(aes(x=counterbalancing, -->
<!--                    y=mean_chose_towards_highdim)) + -->
<!--         geom_violin(fill = chose_highdim_color, -->
<!--                     alpha = 0.2) + -->
<!--         geom_boxplot(width=0.15, -->
<!--                      outlier.shape = '',  -->
<!--                      fatten = 4) + -->
<!--         geom_jitter(width = 0.05, -->
<!--                     height = 0, -->
<!--                     alpha = 0.3) + -->
<!--         stat_summary(fun = mean, -->
<!--                      color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +  -->
<!--         stat_summary(fun.data = mean_cl_normal, -->
<!--                      geom = "errorbar", -->
<!--                      size=0.5, -->
<!--                      width=0.1, -->
<!--                      color='red') +  -->
<!--         coord_cartesian(ylim = ylimits) +  -->
<!--         facet_grid(template_distances~curve_type) + -->
<!--         ggtitle('Chose towards high dimension') -->

<!-- # fig3 <- tt_participant_summary_stats_curve_type_template %>% -->
<!-- #         filter(dep_var_type == 'post_pre_diff') %>% -->
<!-- #         ggplot(aes(x=counterbalancing, -->
<!-- #                    y=mean_correct)) + -->
<!-- #         geom_violin(fill = accuracy_color, -->
<!-- #                     alpha = 0.2) + -->
<!-- #         geom_boxplot(width=0.15, -->
<!-- #                      outlier.shape = '',  -->
<!-- #                      fatten = 4) + -->
<!-- #         geom_jitter(width = 0.05, -->
<!-- #                     height = 0, -->
<!-- #                     alpha = 0.3) + -->
<!-- #         stat_summary(fun = mean, -->
<!-- #                      color = 'red') + geom_hline(yintercept = 0, linetype = 'dashed') +  -->
<!-- #         stat_summary(fun.data = mean_cl_normal, -->
<!-- #                      geom = "errorbar", -->
<!-- #                      size=0.5, -->
<!-- #                      width=0.1, -->
<!-- #                      color='red') +  -->
<!-- #         coord_cartesian(ylim = ylimits) +  -->
<!-- #         facet_grid(template_distances~curve_type) + -->
<!-- #         ggtitle('Accuracy') -->


<!-- grid.arrange(fig1,fig2, -->
<!--              # fig4,fig5,fig6, -->
<!--              ncol = 1, -->
<!--              top = 'Post minus pre') -->

<!-- ``` -->















