---
title: "TT Choice consistency"
output:
  html_document:
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-libraries}

# Clean the environment and load libraries ############################

rm(list=ls())

pacman::p_load(pacman,
               rio,
               tidyverse,
               rstatix,
               DT,
               kableExtra,
               readr,
               writexl,
               jsonlite,
               stringr,
               gridExtra,
               knitr,
               magrittr,
               Hmisc,
               psycho)

```

```{r load-transform-tt-data}

qc_filter = T

source('./scripts/utils/load_transform_tt_data.R')


# load_transform_tt_data(qc_filter)

```


# Choice consistency

## Choice consistency by density space

This is the main question that we're interested in! If choices do not change pre-post, then other dependent variables won't change either.

```{r choice-consistency-by-density, fig.height=5}

# Calculate participant means first
tt_long_post_pre_choice_sum %>%
        group_by(prolific_id,
                 triplet_location,
                 choice_sum_cross_reps_var_type) %>%
        summarise(n = n(),
                  mean = mean(choice_sum_cross_reps_values),
                  sd = sd(choice_sum_cross_reps_values)) %>%
        ggplot(aes(x=choice_sum_cross_reps_var_type,
                   y=mean)) +
        geom_violin() +
        geom_boxplot(width = 0.2,
                     fatten=4,
                     outlier.shape = '') +
        geom_jitter(shape = 21, 
                    fill = 'skyblue',
                    width=0.2,
                    height = 0) + 
        stat_summary(fun=mean, 
                     geom="point", 
                     shape=20,
                     size=5, 
                     color="red", 
                     fill="red") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='red') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        facet_wrap(~triplet_location) +
        
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
        ylab('Choices summed across reps') + 
        coord_cartesian(ylim = c(-2,4)) +
        ggtitle('Choice Consistency Pre, Post and Post-Pre') + 
        xlab('')

```

Plot only the difference values:

We see that when averaging everything, all counterbalancing conditions and all template types, there is potentially an effect. The triplets that are in the middle of the space, i.e. cut across the density boundary.

A negative value on the Y axis means that post-exposure they chose the high-dimension stimuli more often than pre-exposure. But why would both counterbalancing groups choose 

```{r choice-consistency-by-density-only-diff}

# Calculate participant means first
tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff') %>%
        group_by(prolific_id,
                 triplet_location,
                 choice_sum_cross_reps_var_type) %>%
        summarise(n = n(),
                  mean = mean(choice_sum_cross_reps_values),
                  sd = sd(choice_sum_cross_reps_values)) %>%
        ggplot(aes(x=triplet_location,
                   y=mean)) +
        geom_violin() +
        geom_boxplot(width = 0.2,
                     fatten=4,
                     outlier.shape = '') +
        # geom_jitter(shape = 21, fill = 'skyblue',width=0.2) + 
        geom_point() +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +
        stat_summary(fun=mean, 
                     geom="point", 
                     shape=20,
                     size=5, 
                     color="red", 
                     fill="red") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='red') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
        ylab('Choices summed across reps') + 
        ggtitle('Choice Consistency Post-Pre') + 
        xlab('')

```


Does this depend on counterbalancing? Seems like it does!

```{r choice-consistency-by-density-split-cb, fig.height=5, fig.width=10}

tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff') %>%
        group_by(counterbalancing,
                 prolific_id,
                 triplet_location,
                 choice_sum_cross_reps_var_type) %>%
        summarise(n = n(),
                  mean = mean(choice_sum_cross_reps_values),
                  sd = sd(choice_sum_cross_reps_values)) %>%
        ggplot(aes(x=triplet_location,
                   y=mean)) +
        geom_violin() +
        geom_boxplot(width = 0.2,
                     fatten=4,
                     outlier.shape = '') +
        # geom_jitter(shape = 21, fill = 'skyblue',width=0.2) + 
        geom_point() +
        geom_line(aes(group=prolific_id),
                  alpha = 0.2) +
        stat_summary(fun=mean, 
                     geom="point", 
                     shape=20,
                     size=5, 
                     color="red", 
                     fill="red") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='red') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
        ylab('Choices summed across reps') + 
        ggtitle('Choice Consistency Post-Pre') + 
        xlab('') +
        facet_wrap(~counterbalancing)

```

```{r consistency-by-template-triplet-location, fig.height=10, fig.width=8}

# Triplet easiness = 0

fig1 <- tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff',
               triplet_easiness == 0) %>%
        ggplot(aes(x=triplet_location,
                   y=choice_sum_cross_reps_values)) +
        geom_violin() +
        geom_boxplot(width = 0.2,
                     fatten=5,
                     outlier.shape = NA) +
        geom_jitter(width=0.1,
                    height = 0,
                    shape = 21,
                    fill = 'skyblue') +
        geom_hline(yintercept = 0,
                   linetype = 'dashed') +
        facet_wrap(~template_distances) +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
        theme(axis.text.x = element_blank()) +        
        ylab('Pre - post') + 
        xlab('') +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="red", fill="red") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='red')+ 
        ggtitle('Symmetric trials') + 
        xlab('')

fig2 <- tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff',
               triplet_easiness == 8) %>%
        ggplot(aes(x=triplet_location,
                   y=choice_sum_cross_reps_values)) +
        geom_violin() +
        geom_boxplot(width = 0.2,
                     fatten=5,
                     outlier.shape = NA) +
        geom_jitter(width=0.1,
                    height = 0,
                    shape = 21,
                    fill = 'skyblue') +
        geom_hline(yintercept = 0,
                   linetype = 'dashed') +
        facet_wrap(~template_distances, nrow = 1) +
        # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
        theme(axis.text.x = element_blank()) +      
        ylab('Pre - post') + 
        xlab('') +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="red", fill="red") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='red')+ 
        ggtitle('Triplet easiness = 8') + 
        xlab('')

fig3 <- tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff',
               triplet_easiness == 16) %>%
        ggplot(aes(x=triplet_location,
                   y=choice_sum_cross_reps_values)) +
        geom_violin() +
        geom_boxplot(width = 0.2,
                     fatten=5,
                     outlier.shape = NA) +
        geom_jitter(width=0.1,
                    height = 0,
                    shape = 21,
                    fill = 'skyblue') +
        geom_hline(yintercept = 0,
                   linetype = 'dashed') +
        facet_wrap(~template_distances, nrow = 1) +
        # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
        ylab('Pre - post') + 
        xlab('') +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="red", fill="red") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='red')+ 
        ggtitle('Triplet easiness = 16') + 
        xlab('')
        
        grid.arrange(fig1,fig2,fig3,
                     ncol = 1,
                     top='Choice consistency')

# 
# tt_sum_stat_post_pre_choice_sum %>%
#         filter(choice_sum_cross_reps_var_type == 'post_pre_diff_choice_sum_cross_reps') %>%
#         ggplot(aes(x='',
#                    y=mean)) +
#         geom_violin() +
#         geom_boxplot(width = 0.2,fatten=5,outlier.shape = NA) +
#         geom_jitter(width=0.1,shape = 21, fill = 'skyblue') +
#         geom_hline(yintercept = 0, linetype = 'dashed') +
#         facet_grid(template_distances~triplet_location) +
#         theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
#         ylab('Pre - post') + 
#         xlab('') +
#         stat_summary(fun=mean, geom="point", shape=20, size=5, 
#                      color="red", fill="red") + 
#         stat_summary(fun.data = mean_cl_normal,
#                      geom = "errorbar",size=1,width=0.1,color='red')+ 
#         ggtitle('Choice consistency by template and trial stage') + 
#         xlab('')


```

## consistency and curve?

What effect does convexity have? This is pooling across all the participants, in both counterbalancing conditions.


I categorized curvature in the following way:

- Convex: 30-70
- Concave: 70-118

``` {r curvature-consistency}

# Overall consistency by curvature
tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff') %>% 
        group_by(counterbalancing,
                 prolific_id,
                 curve_type) %>%
        summarise(mean = mean(choice_sum_cross_reps_values),
                  n = n()) %>%
        ggplot(aes(x=curve_type,
                   y=mean)) + 
        geom_violin() +
        geom_dotplot(binaxis='y',
                     stackdir='center',
                     stackratio=1,
                     dotsize=0.5,
                     fill="black") +
        # geom_point() + 
        geom_line(aes(group=prolific_id,
                      color=prolific_id)) +
        ylab('Post-pre variability') + 
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='blue') + 
        ggtitle('Overall consistency by curvature') + 
        xlab('') + 
        theme(legend.position = '') +
        geom_hline(yintercept = 0, linetype = 'dashed')

# Overall consistency by curvature
tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff') %>% 
        group_by(counterbalancing,
                 prolific_id,
                 curve_type) %>%
        summarise(mean = mean(choice_sum_cross_reps_values),
                  n = n()) %>%
        ggplot(aes(x=curve_type,
                   y=mean)) + 
        geom_violin() +
        geom_dotplot(binaxis='y',
                     stackdir='centerwhole',
                     stackratio=1, 
                     dotsize=0.5, 
                     fill="black") + 
        geom_line(aes(group=prolific_id,
                      color=prolific_id)) +
        ylab('Post-pre Variability') + 
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='blue') + 
        ggtitle('Overall consistency by curvature AND CB condition') + 
        xlab('') + 
        theme(legend.position = '') +
        facet_wrap(~counterbalancing) +
        geom_hline(yintercept = 0, linetype = 'dashed')


```


## Between participant comparison

```{r between-participant-compare-same-triplet1}

easiness <- 0

fig1 <- tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff',
               triplet_location != 'across_density_regions',
               curve_type == 'concave',
               triplet_easiness == easiness) %>%
        ggplot(aes(x=counterbalancing,
                   y=choice_sum_cross_reps_values)) +
        geom_boxplot(outlier.shape = '',
                     width = 0.3,
                     fatten = 4) +
        geom_jitter(width=0.1,
                    height = 0,
                    alpha=0.3) + 
        facet_wrap(~triplet_unique_name) +
        # facet_grid(~triplet_uniqu) +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='blue') +
        geom_hline(yintercept = 0,
                   linetype = 'dashed') +
        ggtitle('Consistency: Concave, symmetric triplets')

print(fig1)

fig2 <- tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff',
               triplet_location != 'across_density_regions',
               curve_type == 'convex',
               triplet_easiness == easiness) %>%
        ggplot(aes(x=counterbalancing,
                   y=choice_sum_cross_reps_values)) +
        geom_boxplot(outlier.shape = '',
                     width = 0.3,
                     fatten = 4) +
        geom_jitter(width=0.1,
                    height = 0,
                    alpha=0.3) + 
        facet_wrap(~triplet_unique_name) +
        # facet_grid(~triplet_uniqu) +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='blue') +
        geom_hline(yintercept = 0,
                   linetype = 'dashed') +
        ggtitle('Consistency: Convex, symmetric triplets')

print(fig2)

fig3 <- tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff',
               triplet_location != 'across_density_regions',
               curve_type == 'convex',
               triplet_easiness == easiness) %>%
        ggplot(aes(x=counterbalancing,
                   y=choice_sum_cross_reps_values)) +
        geom_boxplot(outlier.shape = '',
                     width = 0.3,
                     fatten = 4) +
        geom_jitter(width=0.1,
                    height = 0,
                    alpha=0.3) + 
        facet_wrap(~template_distances) +
        # facet_grid(~triplet_uniqu) +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='blue') +
        geom_hline(yintercept = 0,
                   linetype = 'dashed') +
        ggtitle('Consistency: Convex, symmetric templates')

print(fig3)

fig4 <- tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff',
               triplet_location != 'across_density_regions',
               curve_type == 'concave',
               triplet_easiness == easiness) %>%
        ggplot(aes(x=counterbalancing,
                   y=choice_sum_cross_reps_values)) +
        geom_boxplot(outlier.shape = '',
                     width = 0.3,
                     fatten = 4) +
        geom_jitter(width=0.1,
                    height = 0,
                    alpha=0.3) + 
        facet_wrap(~template_distances) +
        # facet_grid(~triplet_uniqu) +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='blue') +
        geom_hline(yintercept = 0,
                   linetype = 'dashed') +
        ggtitle('Consistency: Concave, symmetric templates')

print(fig4)

fig5 <- tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff',
               triplet_easiness == easiness) %>%
        ggplot(aes(x=counterbalancing,
                   y=choice_sum_cross_reps_values)) +
        geom_boxplot(outlier.shape = '',
                     width = 0.3,
                     fatten = 4) +
        geom_jitter(width=0.1,
                    height = 0,
                    alpha=0.3) + 
        facet_wrap(~template_distances) +
        # facet_grid(~triplet_uniqu) +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='blue') +
        geom_hline(yintercept = 0,
                   linetype = 'dashed') +
        ggtitle('Consistency: Whole space, symmetric templates')

print(fig5)

```

```{r between-participant-compare-same-triplet2}

easiness <- 8

fig1 <- tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff',
               triplet_location != 'across_density_regions',
               curve_type == 'concave',
               triplet_easiness == easiness) %>%
        ggplot(aes(x=counterbalancing,
                   y=choice_sum_cross_reps_values)) +
        geom_boxplot(outlier.shape = '',
                     width = 0.3,
                     fatten = 4) +
        geom_jitter(width=0.1,
                    height = 0,
                    alpha=0.3) + 
        facet_wrap(~triplet_unique_name) +
        # facet_grid(~triplet_uniqu) +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='blue') +
        geom_hline(yintercept = 0,
                   linetype = 'dashed') +
        ggtitle(paste0('Consistency: Concave, triplet easiness = ',easiness))

print(fig1)

fig2 <- tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff',
               triplet_location != 'across_density_regions',
               curve_type == 'convex',
               triplet_easiness == easiness) %>%
        ggplot(aes(x=counterbalancing,
                   y=choice_sum_cross_reps_values)) +
        geom_boxplot(outlier.shape = '',
                     width = 0.3,
                     fatten = 4) +
        geom_jitter(width=0.1,
                    height = 0,
                    alpha=0.3) + 
        facet_wrap(~triplet_unique_name) +
        # facet_grid(~triplet_uniqu) +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='blue') +
        geom_hline(yintercept = 0,
                   linetype = 'dashed') +
        ggtitle(paste0('Consistency: convex, triplet easiness = ',easiness))

print(fig2)

fig3 <- tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff',
               triplet_location != 'across_density_regions',
               curve_type == 'convex',
               triplet_easiness == easiness) %>%
        ggplot(aes(x=counterbalancing,
                   y=choice_sum_cross_reps_values)) +
        geom_boxplot(outlier.shape = '',
                     width = 0.3,
                     fatten = 4) +
        geom_jitter(width=0.1,
                    height = 0,
                    alpha=0.3) + 
        facet_wrap(~template_distances) +
        # facet_grid(~triplet_uniqu) +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='blue') +
        geom_hline(yintercept = 0,
                   linetype = 'dashed') +
        ggtitle(paste0('Consistency: convex, triplet easiness = ',easiness))

print(fig3)

fig4 <- tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff',
               triplet_location != 'across_density_regions',
               curve_type == 'concave',
               triplet_easiness == easiness) %>%
        ggplot(aes(x=counterbalancing,
                   y=choice_sum_cross_reps_values)) +
        geom_boxplot(outlier.shape = '',
                     width = 0.3,
                     fatten = 4) +
        geom_jitter(width=0.1,
                    height = 0,
                    alpha=0.3) + 
        facet_wrap(~template_distances) +
        # facet_grid(~triplet_uniqu) +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='blue') +
        geom_hline(yintercept = 0,
                   linetype = 'dashed') +
        ggtitle(paste0('Consistency: concave, triplet easiness = ',easiness))

print(fig4)

fig5 <- tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff',
               triplet_easiness == easiness) %>%
        ggplot(aes(x=counterbalancing,
                   y=choice_sum_cross_reps_values)) +
        geom_boxplot(outlier.shape = '',
                     width = 0.3,
                     fatten = 4) +
        geom_jitter(width=0.1,
                    height = 0,
                    alpha=0.3) + 
        facet_wrap(~template_distances) +
        # facet_grid(~triplet_uniqu) +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='blue') +
        geom_hline(yintercept = 0,
                   linetype = 'dashed') +
        ggtitle(paste0('Consistency: whole space, triplet easiness = ',easiness))

print(fig5)

```


```{r between-participant-compare-same-triplet3}

easiness <- 8

fig1 <- tt_long_post_pre_choice_sum %>%
        filter(choice_sum_cross_reps_var_type == 'post_pre_diff',
               # triplet_easiness == easiness,
               triplet_location == 'across_density_regions') %>%
        ggplot(aes(x=counterbalancing,
                   y=choice_sum_cross_reps_values)) +
        geom_violin() +
        geom_boxplot(outlier.shape = '',
                     width = 0.25,
                     fatten = 4) +
        geom_jitter(width=0.1,
                    height = 0,
                    alpha=0.3) + 
        facet_wrap(~triplet_easiness) +
        # facet_grid(~triplet_uniqu) +
        stat_summary(fun=mean, 
                     geom="point",
                     shape=20, 
                     size=5, 
                     color="blue",
                     fill="blue") + 
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",
                     size=1,
                     width=0.1,
                     color='blue') +
        geom_hline(yintercept = 0,
                   linetype = 'dashed') +
        ggtitle(paste0('Consistency: across-density-location, triplet easiness = ',easiness))

print(fig1)

```

